\documentclass[11pt,letterpaper,sans]{moderncv} 

\moderncvstyle{classic}
\moderncvcolor{blue}

\usepackage[scale=0.85]{geometry} 

\firstname{Parth}
\familyname{Mehrotra}

\mobile{9738090571}
\email{parth@mehrotra.me}

\homepage{http://parthmehrotra.com}{parthmehrotra.com}

\begin{document}
\quote{The main stuff}

\makecvtitle


\section{Experience}

\cventry{2015--2018}{Software Engineering Intern}{SAP Labs}{\hfill May, 2015 -- Present}{}{
	\begin{itemize}
		\item SAP Consumer Insights 365 -- a big data solution that allows market researchers to gain unique consumer insights by analyzing terabytes of data. My work on CI365 has been in many cross functional areas of it's technical stack.
		\begin{itemize}
			\item Front-end development: create simple ways our users could craft meaningful queries, and come up with the most useful visualization of that data.
			\item Back-end development: take strategies that our data scientists created and turn them into code with tight performance requirements
			\item Data Science: Wrote machine learning algorithms that helped predict missing attributes of our data.
		\end{itemize}
		\item Authored Data Visualization Suite for Massive Geospatial Dataasets
			\begin{itemize}
				\item A toolset that allowed CI365 data scientists to visualize our data with high fidelity to identify areas of undercoverage/overcoverage.
			\end{itemize}
		\item SAP Multi-Factor Authentication Solutions
			\begin{itemize}
				\item Implemented a TOTP two-factor authentication strategy that allowed us to utilize industry tools (Google Authenticator)
				\item Experimented with novel mutli-factor authentication strategies that utilized push notifications and biometrics.
			\end{itemize}
		\item Led Code Insights Initiative
			\begin{itemize}
				\item  Code Insights is a tool based approach to improving code quality within very large codebases with many contributors.
				\item Programatically converts version controlled codebases into custom Abstract Syntax Trees which are used to track KPI's for each developer.
				\item Pending addition to SAP's collection of Open Source Software.
			\end{itemize}
	\end{itemize}
}

\cventry{2014--2018}{Founder}{AutoAI}{\hfill Oct 2014 -- Present}{}{
	\begin{itemize}
		\item Founded a research project at Rutgers University to create an open source self driving car platform
		\item Led technical, administrative and fundraising efforts.
		\item On track to be a self sufficient, well funded Student Organization at Rutgers University. \
		\item Provides a mechanism for new students to explore applications of advanced topics in computer science under the guidance of experienced members and Rutgers faculty.
		\item Formerly known as DriveAI.
	\end{itemize}
}

\section{Academics}

\cventry{2014--2018}{B.S. Computer Science}{Rutgers University, New Brunswick}{}{}{
	\begin{itemize}
		\item Pursuing B.S. in Computer Science.
		\item Advanced Coursework in Data Structures, Algorithms, Computer Architecture, Systems Engineering, Principals of Programming Languages, Internet Technologies, and Software Methodology. 
		\item Conducted an Independant Study with Professor Peter Jin (Intelligent Transportation Systems) and Professor Kostas Bekris (Artificial Intelligence) with a focus on Self Driving Cars. Where I explored ways we can use sensor fusion to bring down the cost of the AutoAI vehicles. 
	\end{itemize}
}

\cventry{2010--2014}{Graduated High School}{Wayne Hills High School}{}{}{
	\begin{itemize}
		\item During High School I began to really enjoy Math and Computer Science. I started learning Android Development and Robotics during 2010, and I worked on several small apps and websites to help the groups around me. I also completed Advanced Placement coursework in the fields of Physics, Math, Statistics and Computer Science. 
		% \item I also had the pleasure of building leadership exerience by teaching Martial Arts to young children, being the co-captain of the Men's Varsity Swim team, and the Drum Lieutenant of Drumline within the Marching Band.
	\end{itemize}
}

\section{Everything Else}
	\cventry{}{\link{parthmehrotra.com}}{}{}{}{
		I enjoy learning new things, and many of the things I explore are realized in the form of small projects that I publish on my personal website. 
	}

%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

%\clearpage

%\recipient{HR Departmnet}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
%\date{\today} % Letter date
%\opening{Dear Sir or Madam,} % Opening greeting
%\closing{Sincerely yours,} % Closing phrase
%\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents

%\makelettertitle % Print letter title

%\lipsum[1-3] % Dummy text

%\makeletterclosing % Print letter signature

%----------------------------------------------------------------------------------------

\end{document}
